TODO LIST

### 2019-02-27 LMCS/sendrev/framework.tex
sc

The syntax of QSO formulae is divided in two levels. 
The first level is composed by $\so$-formulae over $\R$ (called Boolean formulae) and the second level is made by counting operators of addition and multiplication. 
For this reason, the quantifiers in $\so$ (e.g. $\exists x$ or $\exists X$) are called Boolean quantifiers and the quantifiers that make use of addition and multiplication (e.g. $\Sigma x$ or $\Pi X$) are called {\em quantitative quantifiers}.
Furthermore, $\Sigma x$ and $\Sigma X$ are called first- and second-order sum, whereas $\Pi x$ and $\Pi X$ are called first- and second-order product, respectively.
%This division between Boolean and quantitative level is essential for understanding the difference between the logic and the quantitative part. 
This separation between the Boolean and quantitative levels is essential for understanding the difference between the logic and the quantitative halves of the framework.
\martin{creo que eso quer\'ia decir esta oraci\'on}
Furthermore, this will later allow us to parametrize both levels of the logic in order to capture different counting complexity classes.

>>>>

The syntax of QSO formulae is divided in two levels. 
The first level is composed by $\so$-formulae over $\R$ (called Boolean formulae) and the second level is made by counting operators of addition and multiplication. 
For this reason, the quantifiers in $\so$ (e.g. $\exists x$ or $\exists X$) are called Boolean quantifiers and the quantifiers that make use of addition and multiplication (e.g. $\Sigma x$ or $\Pi X$) are called {\em quantitative quantifiers}.
Furthermore, $\Sigma x$ and $\Sigma X$ are called first- and second-order sum, whereas $\Pi x$ and $\Pi X$ are called first- and second-order product, respectively.
%This division between Boolean and quantitative level is essential for understanding the difference between the logic and the quantitative part. 
This separation between the Boolean and quantitative levels is essential for understanding the difference between the logic and the quantitative parts of the framework.
\martin{creo que eso quer\'ia decir esta oraci\'on}
\marcelo{OK}
Furthermore, this will later allow us to parametrize both levels of the logic in order to capture different counting complexity classes.
